\documentclass[../../main.tex]{subfiles}

\begin{document}

\subsubsection{Appendix F1: Camryn Klintworth}

\paragraph{Principles}
Camryn Klintworth demonstrated the ability to identify, formulate, and solve complex engineering problems by applying principles of engineering, science, and mathematics. He applied theoretical knowledge from coursework in embedded systems, circuit analysis, and digital communication to implement robust solutions involving power regulation, USB interfaces, and memory integration.

\paragraph{Design}
Camryn contributed to the engineering design of a modular embedded system, including a Low Dropout Regulator (LDO) that met specific project requirements in cost, safety, and data reliability. His design approach considered public health and safety, environmental constraints, and long-term usability, aligning with IEEE standards and promoting accessible and reusable hardware architecture.

\paragraph{Communication}
Camryn effectively communicated technical information across written documentation, presentations, and team meetings. He contributed to drafting the final report, explaining design decisions during formal presentations, and regularly collaborating with both faculty and team members to ensure shared understanding and project alignment.

\paragraph{Professionalism}
Camryn consistently recognized and upheld their ethical and professional responsibilities throughout the design process. He made informed judgments that prioritized safety and transparency, particularly in areas involving sensor integration and compliance with IEEE 1789-2015 standards for lighting modulation.

\paragraph{Teamwork}
Camryn functioned effectively within the project team, contributing to collaborative discussions, task execution, and mutual problem-solving. He participated in hardware and software integration, helped coordinate progress across the team, and supported the team in reaching its defined goals and deadlines.

\paragraph{Analysis}
Camryn played an active role in developing and conducting testing procedures, interpreting oscilloscope and logic analyzer data, and validating system performance against success criteria. He applied engineering judgment to draw conclusions about system behavior and inform iterative improvements.

\paragraph{Learning}
Camryn acquired and applied new technical knowledge throughout the project. He independently researched USB communication protocols, AutoCAD techniques, and component behavior using technical references and datasheets, demonstrating adaptability and effective learning strategies.



\end{document}
