\documentclass[../../main.tex]{subfiles}

\begin{document}

\subsubsection{Appendix F1: Carter Brehm}

% an ability to identify, formulate, and solve complex engineering problems by applying principles of engineering, science, and mathematics.
\paragraph{Principles} Carter demonstrated an ability to identify, formulate, and solve complex engineering problems throughout the Harm Drone project. Carter helped to identify solutions to the complex engineering problem through a cooperation of hardware and software. Carter applied principles of embedded systems engineering as well as computer science to write a robust, modular software architecture. Carter also applied concepts of continuous integration to version-control outputs and prevent regression.


% an ability to apply engineering design to produce solutions that meet specified needs with consideration of public health, safety, and welfare, as well as global, cultural, social, environmental, and economic factors.
\paragraph{Design} Carter applied the design principles of engineering to produce solutions that met the specified needs. Throughout the PCB design process, Carter considered safety factors such as the acceptable light wavelengths for human eyesight and electromagnetic disturbance minimization. The software design is divided into modules that can be independently operated and serviced to provide maximum utility in other global, cultural, or economic scenarios.


% an ability to communicate effectively with a range of audiences.
\paragraph{Communication} Carter demonstrated effective communication with various audiences throughout the project. Carter communicated effective technical design to the hardware and system engineer to ensure device driver compatibility with software systems. A comprehensive software design report was presented to the sponsor to gauge alignment and elicit actionable feedback for further interface design. Finally, this software design report was presented formally to peers and superiors.


% an ability to recognize ethical and professional responsibilities in engineering situations and make informed judgments, which must consider the impact of engineering solutions in global, economic, environmental, and societal contexts.
\paragraph{Professionalism} Carter recognized and acted upon ethical and professional responsibilities. Adhering to the IEEE Code of Ethics, Carter made informed judgements as to the impact of the operation of the drone, including reducing wireless telemetry to reduce privacy risks. Each of the hardware components was evaluated against MIL-HDBK-217F, in a full safety and reliability analysis.


% an ability to function effectively on a team whose members together provide leadership, create a collaborative and inclusive environment, establish goals, plan tasks, and meet objectives.
\paragraph{Teamwork}
Carter regularly collaborated with his teammates, including reliable progress reports and risk advisement. This included effective asynchronous work, ensuring that code was completed before on-site meetings to maximize integration testing with the system engineer. Carter also communicated effective goals and objectives to the resource engineer for progress management.


% an ability to develop and conduct appropriate experimentation, analyze and interpret data, and use engineering judgment to draw conclusions.
\paragraph{Analysis} Carter demonstrated the ability to conduct experimentation, analysis, and interpretation of engineering concepts. When designing the communication signals for the universal serial bus, Carter ensured compliance with capacitive and resistive specifications based off manufacturer datasheets as well as implementation-specific calculated values. Carter also facilitated and used tools such as serial-wire debugging to systematically analyze firmware when traditional log output was unavailable.


% an ability to acquire and apply new knowledge as needed, using appropriate learning strategies.
\paragraph{Learning} Carter demonstrated the ability to acquire new knowledge throughout the project, building on knowledge retained from previous engineering courses. To ensure availability of data, Carter researched and implemented a compatible filesystem built on the serial peripheral interface bus. This used a novel alternate mode on most consumer SD cards. Carter also gained valuable knowledge working close with teammates from alternate disciplines, including optimizing power usage with the hardware engineer.


\end{document}
