\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{titling}

\pagestyle{fancy}
\fancyhf{}
\lhead{University of Nebraska--Lincoln}
\rhead{Department of Electrical \& Computer Engineering}
\cfoot{\thepage}

\begin{document}

\begin{center}
    \large \textbf{Capstone Project Completion and Sponsor Approval Letter}
\end{center}

\vspace{1em}

\noindent\textbf{Project Title:} \textit{The Harm Drone: Modular PCB Data Logging System} \\
\textbf{Team Members:} Carter Brehm, Toby Heinemann, Michael Maline, Camryn Klintworth \\
\textbf{Sponsor:} Dr. Andrew Harms \\
\textbf{SPO:} Herb Detloff \\
\textbf{Course:} ECEN 4960/4970 – Senior Design Capstone \\
\textbf{Date:} \today

\vspace{1.5em}

\noindent Dear Dr. Harms,

\vspace{1em}

On behalf of our capstone team, we respectfully submit this letter to acknowledge completing our senior design project, \textit{The Harm Drone}. This embedded system project was developed with your guidance and sponsorship, and its design objectives were defined in alignment with your initial expectations and vision.

The final deliverables encompass all required features, including:
\begin{itemize}
   \item The board will receive and store 1000KB of flight, log, and sensor data on nonvolatile, persistent onboard storage. 
    \item The board will store 4GB of data on a removable SD card in a filesystem format readable on macOS, Windows, and Debian Linux. 
    \item The board will support bi-directional USB communication with up to four sensors.
    \item The drone will contain a removable storage medium that will store up to 4GB of data.
    \item The drone’s lighting system will comply with IEEE 1789-2015 Recommended Practice 2.
\end{itemize}

We are confident that the completed system fulfills the scope and intent originally proposed.

In addition, we express our sincere gratitude for the financial and material support provided through your lab. The resources enabled us to realize the technical objectives of our system fully. Although one of the drone units used for testing was unfortunately lost during the project, we have made every effort to ensure that your lab is fully restored.

We greatly appreciate your understanding and continued mentorship. Please indicate your \\
satisfaction with the project results and confirm that the lab has been restored to your standards by signing the document on the next page.

\newpage

\noindent\textbf{Sponsor and SPO Acknowledgment and Approval:}

\vspace{2em}

\noindent\makebox[2.5in]{\hrulefill} \\
\textbf{Dr. Andrew Harms} \\
Faculty Sponsor, Department of Electrical \& Computer Engineering

\vspace{2em}

\noindent\makebox[2.5in]{\hrulefill} \\
\textbf{Herb Detloff} \\
Senior Project Officer, Department of Electrical \& Computer Engineering \\
\vspace{0.5em}

\noindent We thank you for your mentorship and support throughout the course of this project.

\vspace{0.5em}

\noindent Sincerely, \\
Group 127

\end{document}
